A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
working on related work with new references (still rough).

%%%%% FEEDBACK TO INCORPORATE, from Serge

%-"security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users’ sexual activities exposed to the public..." I would rewrite this. You don't really mean to say that tracking sexual activity is the *only* privacy and security concern. It's one of many. I would say at the beginning that there are myriad privacy/security concerns, and then go into specific examples (e.g., sex, facial recognition, etc.).
%-I think you might want to motivate this better: why do we need to better understand the threat landscape? (Answer: to focus on the most concerning things and then warn users when they're about to occur or prevent them from happening altogether.)
%-Start a new paragraph before the contribution bullets to say what we actually did. For example, "we surveyed 2,250 Internet users to determine..."
%-For the bullets, these can be made much more concise. I would also frame them in terms of what we found, not what we did. For example, "we found that X% of participants found that Y threats were most concerning..."
%-I would limit these bullets to the top 3-4 most interesting findings that we found.

@@

@@

Much of the previous work addresses the anticipated privacy and security challenges related to mobile and wearable devices from a systems standpoint (e.g.,~\cite{DiPietro}). However, system designs to improve end-user security need to be grounded in user research to better understand end-user concerns. Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

@@

\subsection{Technology Risk Perceptions}
Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits.. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

\subsubsection{Smartphone Scenarios}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions:

@@

>>>>

@@

~\cite{Egelman2015} {\color{red} Serge: talk about this; you wrote it and it's not out yet.}
~\cite{bellotti1993design}: framework for designing for privacy in ubicomp.
~\cite{hong2004privacy}: privacy risk model for ubicomp. 
~\cite{jiang2002approximate}: social privacy model for ubicomp.

@@

Designs to improve end-user security need to be grounded in user research to better understand end-user concerns. Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

@@

~\cite{chin2012measuring}: understanding user attitudes toward security and privacy for smartphones. 
~\cite{felt2012android}: if attention to, understand, and act on permission information during installation.
~\cite{laurier2001people}: Why people say where they are during mobile phone calls
~\cite{palen2000going}: behavior and practice of new mobile phone users

\subsection{User Perceptions and Behaviors}

Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits.. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

~\cite{acquisti2005privacy} Privacy and decision making: ppl lack enough info to make privacy-sensitive decisions; even if, likely to trade off long-term privacy for short-term benefits.
~\cite{jensen2005privacy}: Self-reports versus observed behavior
~\cite{spiekermann2001privacy}: Privacy Preferences Versus Actual Behavior

@@

\subsubsection{Smartphone Scenarios}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]

@@

\section{List of all <data>}
{\color{red} Placeholder for space measuring.} \\[-.8cm]

\begin{small}
\begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
  \item foo
  \item bar
   \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
\end{enumerate}
\end{small}
